HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-16 hermes_paper/hermes_paper.tex
Update Section 3

In the specific application of fashion trends prediction, two main forms of standard weaknesses was detected and defined for an univariate parametric forecast as defined above. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is not mainly know. It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals. First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}

\medskip

\begin{figure}
\centering
\begin{subfigure}{1.\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figure/us_female_shoes}
  \caption{Time series representing a shoes fashion trend for female in The United States}
  \label{fig:introexamples:sub1}
\end{subfigure}
\begin{subfigure}{1.\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{figure/br_female_texture_verticalstripe}
  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil}
  \label{fig:introexamples:sub2}
\end{subfigure}
\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model. \textcolor{red}{Ajouter une legende (courbes et axes) et augmenter la police des ticks en abscisses et ordonnées}}
\label{fig:introexamples}
\end{figure}

@@

\subsection{Translate fashion to data}
\label{sec:dataset:a}
A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc. Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere. To represent finely human behaviors based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations. Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousand of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.

@@

In addition to this paper, a fashion dataset is proposed. It contains an sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. Some sequences show interesting behaviours with sudden changes. They are called them emerging or declining trends depending on the change in direction. A central point of this work is to accurately detect and forecast these trends.

@@

Firstly, numerous social media influencers was selectioned by hand by fashion experts. By aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. we named \textit{fashion-forwards} this first weak signal. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}. 
let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model: 
for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel.

Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers. Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.  Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal. let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Based on them, two inputs for our hybrid model are computed  : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,

\begin{align*}
\ws^{l,n}_{t} = \frac{\ts_t^{l,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{l,n}+\ts_t^{m,n}+\ts_t^{h,n}}
\end{align*}  
values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.

@@

In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{l}$ and $\ws^{h}$ are added. They are frequently sparse for micro trends and they often lack interest in common fashion trends. However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}. \textcolor{red}{as illustrated in Section~\ref{}}.

>>>>

In the specific application of fashion trends prediction, two main forms of standard weaknesses was detected and defined for an univariate parametric forecast as defined above. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is not mainly know. It is on this point that  the new HERMES framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals. First forecast examples of this new hybrid model are given in Figure~\ref{fig:introexamples}.

\begin{figure}
\centering
\begin{subfigure}{1.\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figure/us_female_shoes}
  \caption{Time series representing a shoes fashion trend for female in The United States.}
  \label{fig:introexamples:sub1}
\end{subfigure}
\begin{subfigure}{1.\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figure/br_female_texture_verticalstripe}
  \caption{Time series representing the vertical stipes texture fashion trend for female in Brazil.}
  \label{fig:introexamples:sub2}
\end{subfigure}
\caption{Hermes forecast examples. In green the prediction of the TBATS per-time-series predictors. In red the final forecast of our HERMES hybrid model.}
\label{fig:introexamples}
\end{figure}

@@

\subsection{Translate fashion to data}
\label{sec:dataset:a}
A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc. Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere. To represent finely human behaviors based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations. Analysing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization:sub1}.

@@

We therefore introduce a new dataset for fashion time series forecasting.  It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. For instance, some sequences show complex behaviours with sudden changes. They are called emerging or declining trends depending on the change in direction. A central point of this work is to accurately detect and forecast such trends.

@@

Firstly, numerous social media influencers were selectioned by hand by fashion experts. By aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology than for the main panel descibed in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. We named \textit{fashion-forwards} this first weak signal.  For all trend $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.

Secondly, depending of the number of followers, the general panel of users is divided in three sub-groups: users with less than 1350 followers, users with a number of followers between 1350 and 7000 and users with more than 7000 followers. Repeating the previous methodology on each sub-panel, three normalized time series for each time series are created.  Again, the motivation here is to detect behaviour gaps between different part of the society that could announce bigger changes in the main signal. Let $\ts_t^{\ell,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{\ell,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Two inputs for our hybrid model are computed: for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
\begin{align*}
\ws^{\ell,n}_{t} = \frac{\ts_t^{\ell,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}\,,\quad \ws^{h,n}_{t} = \frac{\ts_t^{h,n}}{\ts_t^{\ell,n}+\ts_t^{m,n}+\ts_t^{h,n}}
\end{align*}  
values close to 0.3 indicate a similar behaviour between the three sub-panels and the general panel.

@@

In addition to the fashion dataset, for each time series, the three weak signals $\ws^{f}$,$\ws^{\ell}$ and $\ws^{h}$ are added. They are frequently sparse for micro trends and they often lack interest in common fashion trends. However, in several examples, they are fundamental to detect the future fashion evolutions, as illustrated in Section~\ref{sec:exp}.
